%-------------------------
% Cover Letter in LaTeX
% Formatting based on Resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=linkblue, urlcolor=linkblue, citecolor=linkblue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[charter]{mathdesign}
\usepackage{xcolor}
\usepackage{ragged2e}
\input{glyphtounicode}

% Define custom blue colors to match PDF
\definecolor{headerblue}{RGB}{37,150,190}
\definecolor{linkblue}{RGB}{0,0,238}



















% EDIT THESE VARIABLES
\newcommand{\companyname}{Tower Research Capital}
\newcommand{\positionname}{Software Developer Intern (Summer 2026)}












\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large\color{black}
}{}{0em}{}[\color{headerblue}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Achal Patel} \\ \vspace{2pt}
    \small \faPhone\ 438-979-5673 $|$ 
    \href{mailto:Achalypatel3403@gmail.com}{\faEnvelope\ \underline{Achalypatel3403@gmail.com}} $|$ 
    \href{https://linkedin.com/in/achal-patel}{\faLinkedin\ \underline{linkedin.com/achal-patel}} $|$
    \href{https://github.com/ac-pate}{\faGithub\ \underline{github.com/ac-pate}}
\end{center}

\vspace{0.4in}

\today

\vspace{0.15in}

Dear Recruiting Team, \\
\textbf{\companyname}

\vspace{0.2in}

\textbf{Subject: Application for \positionname}

\vspace{0.15in}

High-performance engineering requires bridging abstract algorithms with bare-metal reality. At CUARL (Concordia University Aerospace Robotics Lab), I work on research problems where software must be reliable, fast, and practical under real constraints—building end-to-end systems that integrate control logic, real-time data pipelines, and deployed AI models. This experience has shaped how I approach performance optimization, system-level design, and debugging. Combined with my hardware validation background at Microchip Technology, I understand both the physical layer constraints and the algorithmic demands of modern computing. I am applying to \companyname\ because your engineering challenges align with my drive to build solutions that are efficient, robust, and impactful.

\vspace{0.2in}

My skillset spans the full stack. I move seamlessly from low-level C++ drivers and FPGA accelerated inference to designing custom deep learning architectures—proven when I won Canadian Engineering Competition, against the best engineering students form all over the country and when I won a Kaggle RNA Folding class competition against Masters/PhD student with a custom Transformer model. Whether optimizing real-time systems, building parallel processing pipelines, or developing production ML models, I bring an R\&D mindset trained to solve undefined problems and deliver working solutions. I am ready to apply this versatile engineering approach to the challenges at \companyname\.

\vspace{0.2in}

I thrive in environment where performance, intelligence, and and relentless problem-solving define success. I am ready to contribute immediately and grow alongside some of the best engineers in the industry.

\vspace{0.2in}

Sincerely,

\vspace{0.1in}

Achal Patel

\end{document}
