%-------------------------
% Cover Letter in LaTeX
% Formatting based on Resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=linkblue, urlcolor=linkblue, citecolor=linkblue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[charter]{mathdesign}
\usepackage{xcolor}
\usepackage{ragged2e}
\input{glyphtounicode}

% Define custom blue colors to match PDF
\definecolor{headerblue}{RGB}{37,150,190}
\definecolor{linkblue}{RGB}{0,0,238}

% EDIT THESE VARIABLES
\newcommand{\companyname}{[Company ]}
\newcommand{\positionname}{[ghgg]}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large\color{black}
}{}{0em}{}[\color{headerblue}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Achal Patel} \\ \vspace{2pt}
    \small \faPhone\ 438-979-5673 $|$ 
    \href{mailto:Achalypatel3403@gmail.com}{\faEnvelope\ \underline{Achalypatel3403@gmail.com}} $|$ 
    \href{https://linkedin.com/in/achal-patel}{\faLinkedin\ \underline{linkedin.com/achal-patel}} $|$
    \href{https://github.com/ac-pate}{\faGithub\ \underline{github.com/ac-pate}}
\end{center}

\vspace{0.4in}

\today

\vspace{0.15in}

Recruiting Team \\
\textbf{\companyname}

\vspace{0.2in}

\textbf{Subject: Application for \positionname}

\vspace{0.15in}

To Whom It May Concern,
\vspace{0.2in}

\begin{justify}
\hspace{\parindent} My hands-on experience in robotics spans competitive engineering, academic research, and real-world robotic deployments. Beginning the spark for robotics from my first competition and later winning the 2025 Canadian Engineering Competition as National Champions amongst the best of engienering studetns, I made a clear decision, it was robotics or nothing. While my childhood dream was space,  and when I landed a research internship at CUARL (Concordia University Aerospace Robotics Lab)  worked on motion planning, teleoperation, and perception-based localization for articulated rovers, bridging simulation with real hardware. Alongside this, I have completed projects in autonomous robotics, bimanual dexterity, and sensor fusion. I am currently co-leading the MIMIC Capstone Project in collaboration with McGill’s Mobile Robotics Lab, where we are developing bimanual mobile robots that learn from human demonstration using VLA models and imitation learning. My focus is on robotics that combines vision, planning, and sensor-driven intelligence to solve complex real-world problems where performance and reliability matter. I am applying to \companyname\ because your work strongly aligns with both my technical background and my passion.

\vspace{0.2in}

I bring deep technical experience across the full robotics stack. I am well-versed in core robotics tools and frameworks including ROS2 (C++ \& Python), NAV2, MoveIt2, Isaac Lab, and OpenCV, paired with hands-on hardware experience in low-level control, embedded systems, controller design, and FPGA-based acceleration. Beyond technical work, I actively engage in competitive and leadership environments. I previously served as VP of Projects at IEEE Concordia Student Association, where I led multidisciplinary teams working on IoT, drone systems, FPGA projects, and robotic arms. I have also delivered workshops on robotics fundamentals, CAD, and microcontroller programming, apart from tutoring as a Undergraduate Teaching Assistant at Concoridia University. With a strong work ethic, and genuine passion for robotics, I am confident in my ability to add immediate value to \companyname. I would be excited to contribute to your team this summer.
\end{justify}

\vspace{0.2in}

Sincerely,

\vspace{0.1in}

Achal Patel

\end{document}
